---
title: "Week 8"
author: "Section 2"
date: "October 18, 2015"
output: html_document
---
For this project, I created 3 documents using XML, HTML and JSON in a notepad (I have never done this before... My apologies if these documents make no sense, but I copied the basic formats I found via the slide deck from Gaston Sanchez and from Google searches on HTML tables.)

Using the r packages I then uploaded the data using the following packages: 

```{r}
library(XML)
library(RJSONIO)
library(rvest)
library(RCurl)
```

For the week 8 assignment I created the following files: 

```{r}
url_html <- getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/Books.HTML")
url_json <- getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/Books.JSON")
url_xml <- getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/Books.xml")

#Data_XML <- xmlToDataFrame(url_xml)
#Data_JSON <- fromJSON("data/Books.JSON")
Data_HTML <-readHTMLTable("data/Books.HTML")
#Data_XMl
#Data_JSON
Data_HTML

````


As you can see the data is read differently based on the packages (and because it was written slightly different in each type. )