---
title: "Week 8"
author: "Section 2"
date: "October 18, 2015"
output: html_document
---

## XML, HTML and JSON Homework
For this project, I created 3 documents using XML, HTML and JSON in a notepad (I have never done this before... My apologies if these documents are not properly written, but I copied the basic formats I found via the slide deck from Gaston Sanchez and from Google searches on HTML tables.)

Using the r packages I then uploaded the data using the following packages: 

```{r}
library(XML)
library(RJSONIO)
library(rvest)
library(RCurl)
```

For the week 8 assignment I created the following files: 

```{r}
url_html <- getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/Books.HTML")
url_json <- getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/Books.JSON")
url_xml <- getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/Books.xml")

Data_XML <- xmlToDataFrame(url_xml)
#Data_JSON <- fromJSON(url_json)
Data_HTML <-readHTMLTable(url_html)
Data_XML
# I cannot get the JSON to read properly via web... my familiarity with this is quite new. I wrote an appendix section, to show an ouput that I used to "create" a JSON from the HTML data set. It created a similar data frame and and Identical source code. For the life of me I can't figure out why it doesn't read it. 
#Data_JSON
Data_HTML

```


As you can see the data is read differently based on the packages (and because it was written slightly different in each type). One problem I was having (and you can see from the two sources) is that the XML has a subchild, which created multiple Authors, but put them togethere in a single row. For HTML, I couldn't figure out a way to utlized the subchild method, so I created 4 separate authors (I did this with the JSON file as well but like I stated previously, I could not get the file to load, see below). 

## Appendix 
As I couldn't create the JSON file, I took the data.frame I created from the HTML and made a JSON File using the RJSONIO package. See below:  

```{r}
JSON_file  <- toJSON(Data_HTML)
write(JSON_file, "json_file.json")
```

This created a json_file, which I then attempted to load(This looked exactly like mine, maybe I am just tired, and missed a comma somewhere).

```{r}
url_json <-getURL("https://raw.githubusercontent.com/mfarris9505/Week-8-Hwk/master/json_file.json")
Data_JSON <- fromJSON(url_json)
Data_JSON
```

As you can see, the output of this is different than the other two data sources.The other files created a data.frame that was much more tabular, while this one created a less organized file. I wonder if this was more because of the JSON package utilized. The other packages appear to have created a data frame. 
